Bird species composition in coastal urban habitats

### 2020-11-11 Ms_HabitatAves.Rmd
CAmbios pequeños

#Ambos graficos con paquete patchwork
Inv+Prim + plot_annotation(tag_levels = 'A')
```

@@

```{r Comportamineto, fig.height=7, fig.width=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

>>>>

#Ambos graficos con paquete patchwork
Inv+Prim + plot_annotation(tag_levels = 'A')+ plot_layout(guides = 'collect')
```

@@

```{r Comportamineto, fig.height=8, fig.width=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
